### 2020-12-22 paper/localpsf.tex
editing construction section

\subsection{Mean and covariance estimation}
\label{eq:mean_and_covariance_estimation}

Since $\varphi_x$, and thus $\langle\mathcal{A},\delta_{x}\rangle^*$, is nonnegative, $\langle\mathcal{A},\delta_{x}\rangle^*$ is a scaled probability distribution. We compute the scaling factor, denoted $\alpha(x)$, for all $x$ simultaneously by applying $\mathcal{A}$ to a constant function. We then compute the mean, $\mu(x)$, and covariance, $\Sigma(x)$ of the normalized version of $\langle\mathcal{A},\delta_{x}\rangle^*$, for all $x$ simultaneously, by applying $\mathcal{A}^T$ to a small number of linear and quadratic functions. The support of $\langle\mathcal{A},\delta_{x}\rangle^*$ is estimated to be contained in an ellipsoid of points that are within a small number of standard deviations of the mean for a Gaussian distribution with the same mean and covariance as the normalized version of $\langle\mathcal{A},\delta_{x}\rangle^*$.

@@

@@

\begin{prop}
	\label{thm:vol_mean_cov}
	Let  $x^i$ denote the $i^\text{th}$ component of $x$, i.e., $x = \left(x^1, x^2, \dots, x^d\right)$, and let $C$, $\{L^i\}_{i=1}^d$, and ${\{Q^{ij}\}_{i=1}^d}_{j=1}^d$ be the following constant, linear, and quadratic functions, respectively:
	\begin{equation*}
		C(x) := 1, \qquad
		L^i(x) := x^i, \qquad
		Q^{ij}(x) = x^i x^j.
	\end{equation*}
	We have
	\begin{align}
		\alpha =& \left(\mathcal{A}^TC\right)^*, \label{eq:vol_mean_var_thm1}\\
		\mu^i =& \left(\mathcal{A}^T L^i\right)^* / \alpha, \label{eq:vol_mean_var_thm2}\\
		\Sigma^{ij} =& \left(\mathcal{A}^T Q^{ij}\right)^* / \alpha - \mu^i\cdot\mu^j, \label{eq:vol_mean_var_thm3}
	\end{align}
	We write $f/g$ to denote the pointwise division of functions, $\left(f/g\right)(x) = f(x)/g(x)$, and $f\cdot g$ to denote the pointwise multiplication of functions, $(f\cdot g)(x) = f(x)g(x)$.
\end{prop}

@@

Ideally, sample points $x_i$ and $x_j$ should be far enough apart from each other that the supports of $\left\langle\mathcal{A}, \delta_{x_i}\right\rangle^*$ and $\left\langle\mathcal{A}, \delta_{x_j}\right\rangle^*$ do not overlap. Since it is too expensive compute the support of $\left\langle\mathcal{A}, \delta_{x}\right\rangle^*$ directly, we instead estimate that the support of $\left\langle\mathcal{A}, \delta_{x}\right\rangle^*$ is contained in the ellipsoid
\begin{equation}
\label{eq:support_ellipsoid}
	E_x := \{x' \in \Omega: (x' - \mu(x))^T \Sigma(x)^{-1} (x' - \mu(x)) \le \tau^2\},
\end{equation}
where $\tau$ is a small number of standard deviations; we use $\tau=3$. The ellipsoid $E_x$ is the set of points within $\tau$ standard deviations of the mean for the Gaussian distribution that has the same mean and covariance as $\left\langle\mathcal{A}, \delta_{x}\right\rangle^*$. The fraction of the mass of $\left\langle\mathcal{A}, \delta_{x}\right\rangle^*$ residing outside of $E_x$ is less than $1/\tau^2$ by Chebyshev's inequality, though we find this bound is conservative and far less mass resides in this region in practice. 
%We call $E_x$ the \emph{unit ellipsoid} with mean $\mu(x)$ and covariance $\Sigma(x)/\tau^2$.

We select a batch of sample points, $S_b$, randomly from a finite set of candidate points $P$. Starting from an empty set, we build $S_b$ by choosing candidate points $p$ from $P$, one at a time. The current candidate point, $p$, is the point in $P$ that is the farthest away from all points in previous sample point baches. That is, the maximizer of the following optimization problem:
\begin{equation*}
\max_{p \in P} \min_{x \in S_1 \cup \dots \cup S_{b-1}} \|p - x\|
\end{equation*}
After we choose the candidate $p$, we remove $p$ from $P$.
If $p$ is sufficiently far from all of the previously chosen points in the current batch, in the sense that $E_p \cap E_q = \{\}$ for all $q \in S_b$, and if $p$ is sufficiently far from the boundary, in the sense that $E_p \cap \partial \Omega = \{\}$, then we add $p$ to $S_b$. Otherwise we discard $p$. This process repeats until there are no more points in $P$. 
%This is detailed in Algorithm \ref{alg:point_choice}.

>>>>

\subsection{Estimating impulse response supports}
\label{eq:mean_and_covariance_estimation}

Since $\varphi_x$, and thus $\langle\mathcal{A},\delta_{x}\rangle^*$, is nonnegative, $\langle\mathcal{A},\delta_{x}\rangle^*$ is a scaled probability distribution. We compute the scaling factor, denoted $\alpha(x)$, for all $x$ simultaneously by applying $\mathcal{A}$ to a constant function. We then compute the spatially varying mean, $\mu(x)$, and covariance, $\Sigma(x)$ of the normalized version of $\langle\mathcal{A},\delta_{x}\rangle^*$, for all $x$ simultaneously, by applying $\mathcal{A}^T$ to a small number of linear and quadratic functions. We make the approximation that the support of $\langle\mathcal{A},\delta_{x}\rangle^*$ is contained within the ellipsoid
\begin{equation}
\label{eq:support_ellipsoid}
E_x := \{x' \in \Omega: (x' - \mu(x))^T \Sigma(x)^{-1} (x' - \mu(x)) \le \tau^2\},
\end{equation}
where $\tau$ is a small number of standard deviations; we use $\tau=3$. The ellipsoid $E_x$ is the set of points within $\tau$ standard deviations of the mean for the Gaussian distribution that has the same mean and covariance as the normalized version of $\left\langle\mathcal{A}, \delta_{x}\right\rangle^*$. The fraction of the mass of $\left\langle\mathcal{A}, \delta_{x}\right\rangle^*$ residing outside of $E_x$ is less than $1/\tau^2$ by Chebyshev's inequality, though we find this bound is conservative and far less mass resides in this region in practice.

@@

%The support of $\langle\mathcal{A},\delta_{x}\rangle^*$ is estimated to be contained within a small number of standard deviations of the mean for a Gaussian distribution with the same mean and covariance as the normalized version of $\langle\mathcal{A},\delta_{x}\rangle^*$.

@@

\begin{theorem}
	\label{thm:vol_mean_cov}
	Let  $x^i$ denote the $i^\text{th}$ component of $x$, i.e., $x = \left(x^1, x^2, \dots, x^d\right)$, and let $C$, $\{L^i\}_{i=1}^d$, and ${\{Q^{ij}\}_{i=1}^d}_{j=1}^d$ be the following constant, linear, and quadratic functions, respectively:
	\begin{equation*}
		C(x) := 1, \qquad
		L^i(x) := x^i, \qquad
		Q^{ij}(x) = x^i x^j.
	\end{equation*}
	We have
	\begin{align}
		\alpha =& \left(\mathcal{A}^TC\right)^*, \label{eq:vol_mean_var_thm1}\\
		\mu^i =& \left(\mathcal{A}^T L^i\right)^* / \alpha, \label{eq:vol_mean_var_thm2}\\
		\Sigma^{ij} =& \left(\mathcal{A}^T Q^{ij}\right)^* / \alpha - \mu^i\cdot\mu^j, \label{eq:vol_mean_var_thm3}
	\end{align}
	We write $f/g$ to denote the pointwise division of functions, $\left(f/g\right)(x) = f(x)/g(x)$, and $f\cdot g$ to denote the pointwise multiplication of functions, $(f\cdot g)(x) = f(x)g(x)$.
\end{theorem}

@@

Ideally, sample points $x_i$ and $x_j$ should be far enough apart from each other that the supports of $\left\langle\mathcal{A}, \delta_{x_i}\right\rangle^*$ and $\left\langle\mathcal{A}, \delta_{x_j}\right\rangle^*$ do not overlap.

%Since it is too expensive compute the support of $\left\langle\mathcal{A}, \delta_{x}\right\rangle^*$ directly, we instead estimate that the support of $\left\langle\mathcal{A}, \delta_{x}\right\rangle^*$ is contained in the ellipsoid
%\begin{equation}
%\label{eq:support_ellipsoid}
%	E_x := \{x' \in \Omega: (x' - \mu(x))^T \Sigma(x)^{-1} (x' - \mu(x)) \le \tau^2\},
%\end{equation}
%where $\tau$ is a small number of standard deviations; we use $\tau=3$. The ellipsoid $E_x$ is the set of points within $\tau$ standard deviations of the mean for the Gaussian distribution that has the same mean and covariance as $\left\langle\mathcal{A}, \delta_{x}\right\rangle^*$. The fraction of the mass of $\left\langle\mathcal{A}, \delta_{x}\right\rangle^*$ residing outside of $E_x$ is less than $1/\tau^2$ by Chebyshev's inequality, though we find this bound is conservative and far less mass resides in this region in practice.

%We call $E_x$ the \emph{unit ellipsoid} with mean $\mu(x)$ and covariance $\Sigma(x)/\tau^2$.

We select a batch of sample points, $S_b$, randomly from a finite set of candidate points $P$. Starting from an empty set, we build $S_b$ by choosing candidate points $p$ from $P$, one at a time. The current candidate point, $p$, is the point in $P$ that is the farthest away from all points in previous sample point baches. That is, the maximizer of the following optimization problem:
\begin{equation*}
\max_{p \in P} \min_{x \in S_1 \cup \dots \cup S_{b-1}} \|p - x\|.
\end{equation*}
After we choose the candidate $p$, we remove $p$ from $P$.
If $p$ is sufficiently far from all of the previously chosen points in the current batch, in the sense that $E_p \cap E_q = \{\}$ for all $q \in S_b$, and if $p$ is sufficiently far from the boundary, in the sense that $E_p \cap \partial \Omega = \{\}$, then we add $p$ to $S_b$. Otherwise we discard $p$. This process repeats until there are no more points in $P$. 
%This is detailed in Algorithm \ref{alg:point_choice}.
